### 2023-02-02 manuscript.tex
biblatex tests [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/1bb192ee3877d8cf686952ca8a79a62e840c6247.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/1bb192ee3877d8cf686952ca8a79a62e840c6247/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4073836159

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/601c8115352e75e7e5f7ba261f24d27cadfa887a/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/601c8115352e75e7e5f7ba261f24d27cadfa887a}{stain/2022-fdo-paper@601c811}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1bb192ee3877d8cf686952ca8a79a62e840c6247/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1bb192ee3877d8cf686952ca8a79a62e840c6247}{stain/2022-fdo-paper@1bb192e}
on February 2, 2023.
